library("jsonlite")
json_data <- read_json("TrainData\\bump.json")

vector_acceX <- numeric()
vector_acceY <- numeric()
vector_acceZ <- numeric()
vector_acceX_raw <- numeric()
vector_acceY_raw <- numeric()
vector_acceZ_raw <- numeric()
vector_time <- numeric()
vector_gpsSpeed <- numeric()
vector_lat <- numeric()
vector_lon <- numeric()
vector_anomaly <-character()

for (item in json_data){
  vector_acceX <- c(vector_acceX, item$acceX)
  vector_acceY <- c(vector_acceY, item$acceY)
  vector_acceZ <- c(vector_acceZ, item$acceZ)
  vector_acceX_raw <- c(vector_acceX_raw, item$acceX_raw)
  vector_acceY_raw <- c(vector_acceY_raw, item$acceY_raw)
  vector_acceZ_raw <- c(vector_acceZ_raw, item$acceZ_raw)
  vector_time <- c(vector_time, item$time)
  vector_gpsSpeed <- c(vector_gpsSpeed, 10)
  vector_lat <- c(vector_lat, item$lat)
  vector_lon <- c(vector_lon, item$lon)
  vector_anomaly <- c(vector_anomaly, item$anomaly)
}

library(randomForest)
data_set_bump = data.frame(acceY = vector_acceY_raw, acceX = vector_acceX_raw, acceZ = vector_acceZ_raw, speed = vector_gpsSpeed, anomaly = vector_anomaly)  
summary(data_set_bump)
```{r}

library(plotly)
theme_set(theme_classic())
p <- plot_ly(data_set_bump, x = ~time, y = ~acceY, type = "area")
p
```
model_Bump <- randomForest(anomaly ~ ., data = data_set_bump, importance = TRUE)
model_Bump


library("pracma")
bump_movavg_acceY <- movavg(vector_acceY_raw, 100, type=c("s"))
bump_movavg_acceX <- movavg(vector_acceX_raw, 100, type=c("s"))
bump_movavg_acceZ <- movavg(vector_acceZ_raw, 100, type=c("s"))
data_set_movavg_bump = data.frame(acceY = bump_movavg_acceY, acceX = bump_movavg_acceX, acceZ = bump_movavg_acceZ, speed = vector_gpsSpeed, anomaly = vector_anomaly)
summary(data_set_movavg_bump)
```{r}

library(plotly)
theme_set(theme_classic())
p <- plot_ly(data_set_movavg_bump, x = ~time, y = ~acceY, type = "area")
p
```
model_Bump_movavg <- randomForest(anomaly ~ ., data = data_set_movavg_bump, importance = TRUE)
model_Bump_movavg




```{r}
json_data <- read_json("TrainData\\pothole_40kmph.json")

vector_acceX_P <- numeric()
vector_acceY_P <- numeric()
vector_acceZ_P <- numeric()
vector_acceX_raw_P <- numeric()
vector_acceY_raw_P <- numeric()
vector_acceZ_raw_P <- numeric()
vector_time_P <- numeric()
vector_gpsSpeed_P <- numeric()
vector_lat_P <- numeric()
vector_lon_P <- numeric()
vector_anomaly_P <-character()

for (item in json_data){
  vector_acceX_P <- c(vector_acceX_P, item$acceX)
  vector_acceY_P <- c(vector_acceY_P, item$acceY)
  vector_acceZ_P <- c(vector_acceZ_P, item$acceZ)
  vector_acceX_raw_P <- c(vector_acceX_raw_P, item$acceX_raw)
  vector_acceY_raw_P <- c(vector_acceY_raw_P, item$acceY_raw)
  vector_acceZ_raw_P <- c(vector_acceZ_raw_P, item$acceZ_raw)
  vector_time_P <- c(vector_time_P, item$time)
  vector_gpsSpeed_P <- c(vector_gpsSpeed_P, item$gpsSpeed)
  vector_lat_P <- c(vector_lat_P, item$lat)
  vector_lon_P <- c(vector_lon_P, item$lon)
  vector_anomaly_P <- c(vector_anomaly_P, item$anomaly)
}
data_set_Pothole = data.frame(acceY = vector_acceY_raw_P,time = vector_time_P )
theme_set(theme_classic())
p <- plot_ly(data_set_Pothole, x = ~time, y = ~acceY, type = "area")
p
```



json_data <- read_json("TrainData\\pothole_40kmph.json")

for (item in json_data){
  vector_acceX <- c(vector_acceX, item$acceX)
  vector_acceY <- c(vector_acceY, item$acceY)
  vector_acceZ <- c(vector_acceZ, item$acceZ)
  vector_acceX_raw <- c(vector_acceX_raw, item$acceX_raw)
  vector_acceY_raw <- c(vector_acceY_raw, item$acceY_raw)
  vector_acceZ_raw <- c(vector_acceZ_raw, item$acceZ_raw)
  vector_time <- c(vector_time, item$time)
  vector_gpsSpeed <- c(vector_gpsSpeed, item$gpsSpeed)
  vector_lat <- c(vector_lat, item$lat)
  vector_lon <- c(vector_lon, item$lon)
  vector_anomaly <- c(vector_anomaly, item$anomaly)
}
data_set = data.frame(acceY = vector_acceY_raw, acceX = vector_acceX_raw, acceZ = vector_acceZ_raw, speed = vector_gpsSpeed, anomaly = vector_anomaly)

head(data_set)
summary(data_set)

nrow(data_set)


json_data <- read_json("TestData\\HTC-Tida-Walpola-Matara.json")
vector_acceX <- numeric()
vector_acceY <- numeric()
vector_acceZ <- numeric()
vector_acceX_raw <- numeric()
vector_acceY_raw <- numeric()
vector_acceZ_raw <- numeric()
vector_time <- numeric()
vector_gpsSpeed <- numeric()
vector_lat <- numeric()
vector_lon <- numeric()
vector_anomaly <-character()

for (item in json_data){
  vector_acceX <- c(vector_acceX, as.numeric(item$acceX))#check whether input data in required time.
  vector_acceY <- c(vector_acceY, as.numeric(item$acceY))
  vector_acceZ <- c(vector_acceZ, as.numeric(item$acceZ))
  vector_acceX_raw <- c(vector_acceX_raw, item$acceX_raw)
  vector_acceY_raw <- c(vector_acceY_raw, item$acceY_raw)
  vector_acceZ_raw <- c(vector_acceZ_raw, item$acceZ_raw)
  vector_time <- c(vector_time, as.numeric(item$time))
  vector_gpsSpeed <- c(vector_gpsSpeed, item$gpsSpeed)
  vector_lat <- c(vector_lat, item$lat)
  vector_lon <- c(vector_lon, item$lon)
  vector_anomaly <- c(vector_anomaly, item$anomaly)
}

test_data_set = data.frame(acceY = vector_acceY, acceX = vector_acceX, acceZ = vector_acceZ, speed = vector_gpsSpeed)

```{r}
#library(plotly)
theme_set(theme_classic())
test_data_set_graph = data.frame(acceY = vector_acceY, time = vector_time )
p <- plot_ly(test_data_set_graph, x = ~time, y = ~acceY, type = "area")
p
```


nrow(test_data_set)
head(test_data_set)
summary(test_data_set)

head(data_set)
summary(data_set)

library(randomForest)
  
model1 <- randomForest(anomaly ~ ., data = data_set, importance = TRUE)
model1

pred <- predict(model1, test_data_set, type = "class")
pred
nrow(pred)

Pred_Using_Bump_model <- predict(model_Bump, test_data_set, type = "class")
nrow(Pred_Using_Bump_model)

Pred_Using_model_Bump_movavg<- predict(model_Bump_movavg, test_data_set, type = "class")
nrow(Pred_Using_model_Bump_movavg)

result = data.frame(time = vector_time, acceY = vector_acceY, acceX = vector_acceX, acceZ = vector_acceZ, speed = vector_gpsSpeed, anomaly = pred)

result_Using_Bump_model = data.frame(time = vector_time, acceY = vector_acceY, acceX = vector_acceX, acceZ = vector_acceZ, speed = vector_gpsSpeed, anomaly = Pred_Using_Bump_model)

result_Using_model_Bump_movavg = data.frame(time = vector_time, acceY = vector_acceY, acceX = vector_acceX, acceZ = vector_acceZ, speed = vector_gpsSpeed, anomaly = Pred_Using_model_Bump_movavg)

head(result)
summary(result)
nrow(result)

head(result_Using_Bump_model)
summary(result_Using_Bump_model)
nrow(result_Using_Bump_model)

head(result_Using_model_Bump_movavg)
summary(result_Using_model_Bump_movavg)
nrow(result_Using_model_Bump_movavg)


library("jsonlite")
write_json(result, "Prediction\\HTC-Tida-Walpola-Matara.json")

#head(pred)
#summary(pred)



#total_data_set <- merge(valid_data_set, predTrain)
#total_data_set

#summary(total_data_set)

#model2 <- randomForest(anomaly ~ ., data = data_set, ntree = 500, mtry = 6, importance = TRUE)
#model2

#model3 <- randomForest(anomaly ~ ., data = data_set, ntree = 500, mtry = 2, importance = TRUE)
#model3

