library("jsonlite")
json_data <- read_json("TrainData\\bump.json")

vector_acceX <- numeric()
vector_acceY <- numeric()
vector_acceZ <- numeric()
vector_acceX_raw <- numeric()
vector_acceY_raw <- numeric()
vector_acceZ_raw <- numeric()
vector_time <- numeric()
vector_gpsSpeed <- numeric()
vector_lat <- numeric()
vector_lon <- numeric()
vector_anomaly <-character()

for (item in json_data){
  vector_acceX <- c(vector_acceX, item$acceX)
  vector_acceY <- c(vector_acceY, item$acceY)
  vector_acceZ <- c(vector_acceZ, item$acceZ)
  vector_acceX_raw <- c(vector_acceX_raw, item$acceX_raw)
  vector_acceY_raw <- c(vector_acceY_raw, item$acceY_raw)
  vector_acceZ_raw <- c(vector_acceZ_raw, item$acceZ_raw)
  vector_time <- c(vector_time, item$time)
  vector_gpsSpeed <- c(vector_gpsSpeed, 10)
  vector_lat <- c(vector_lat, item$lat)
  vector_lon <- c(vector_lon, item$lon)
  vector_anomaly <- c(vector_anomaly, item$anomaly)
}


```{r}
graph_data = data.frame(time = vector_time, acceY = vector_acceY_raw)
library(plotly)
p <- plot_ly(graph_data, x = ~time, y = ~acceY, type = "area")
p
```

library("pracma")
d_acceY <- diff(vector_acceY)/(diff(vector_time/1000))
d_acceY <- append(0, d_acceY)

```{r}
library("pracma")
d_acceY <- diff(vector_acceY)/(diff(vector_time/1000))
d_acceY <- append(0, d_acceY)
graph_data = data.frame(time = vector_time, d_acceY = d_acceY)
p <- plot_ly(graph_data, x = ~time, y = ~d_acceY, type = "area")
p
```

data_set_bump = data.frame(acceY = d_acceY, acceX = vector_acceX_raw, acceZ = vector_acceZ_raw, speed = vector_gpsSpeed, anomaly = vector_anomaly)  
summary(data_set_bump)

library(randomForest)
model_Bump <- randomForest(anomaly ~ ., data = data_set_bump, importance = TRUE)
model_Bump

json_data <- read_json("TestData\\HTC-Tida-Walpola-Matara.json")
vector_acceX <- numeric()
vector_acceY <- numeric()
vector_acceZ <- numeric()
vector_acceX_raw <- numeric()
vector_acceY_raw <- numeric()
vector_acceZ_raw <- numeric()
vector_time <- numeric()
vector_gpsSpeed <- numeric()
vector_lat <- numeric()
vector_lon <- numeric()
vector_anomaly <-character()

for (item in json_data){
  vector_acceX <- c(vector_acceX, as.numeric(item$acceX))#check whether input data in required time.
  vector_acceY <- c(vector_acceY, as.numeric(item$acceY))
  vector_acceZ <- c(vector_acceZ, as.numeric(item$acceZ))
  vector_acceX_raw <- c(vector_acceX_raw, item$acceX_raw)
  vector_acceY_raw <- c(vector_acceY_raw, item$acceY_raw)
  vector_acceZ_raw <- c(vector_acceZ_raw, item$acceZ_raw)
  vector_time <- c(vector_time, as.numeric(item$time))
  vector_gpsSpeed <- c(vector_gpsSpeed, item$gpsSpeed)
  vector_lat <- c(vector_lat, item$lat)
  vector_lon <- c(vector_lon, item$lon)
  vector_anomaly <- c(vector_anomaly, item$anomaly)
}

test_data_set = data.frame(acceY = vector_acceY, acceX = vector_acceX, acceZ = vector_acceZ, speed = vector_gpsSpeed)

nrow(test_data_set)
head(test_data_set)
summary(test_data_set)

pred <- predict(model_Bump, test_data_set, type = "class")
result = data.frame(time = vector_time, acceY = vector_acceY, acceX = vector_acceX, acceZ = vector_acceZ, speed = vector_gpsSpeed, anomaly = pred)

head(result)
summary(result)
nrow(result)
write_json(result, "Prediction\\HTC-Tida-Walpola-Matara-Trained-for-bumps-using-first-derivative.json")